### 2016-09-10 sec4_baseline.tex
Revise some minor points
Current Version

\begin{figure*} [t]
\center
\includegraphics[width=0.85\textwidth]{trm.eps}
\caption{Work flow of Temporal Replication and Parallel Mining (TRPM). (a) and (b) correspond to the first map-reduce stage which clusters objects in each snapshot.  (c) and (d) correspond to the second map-reduce stage, which uses TRPM to detect GCMP in parallel.}
\label{fig:trm}
\end{figure*}

\section{Baseline: Temporal Replication and Parallel Mining}
\label{sec:trm}
In this section, we propose a baseline solution that resorts to MapReduce (MR) as a general, parallel and scalable paradigm for GCMP mining. The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}. There are two stages of map-reduce jobs connected in a pipeline manner. The first stage deals with spatial clustering of objects in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining phase. In particular, for the first stage, the timestamp is treated as the key in the map phase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phase. Finally, the reducers output clusters of objects in each snapshot, represented by a list of key-value pairs $\langle t, S_t  \rangle$, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.

@@

\begin{theorem}
\label{THM:RP_ETA}
$\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$ guarantees that no valid pattern is missing.
\end{theorem}
\begin{proof}
Given a valid pattern $P$, we can always find at least one valid subsequence of $P.T$ that is also valid. Let $T'$ denote the valid subsequence of $P.T$ with the minimum length. In the worst case, $T'=P.T$. We define $\range(T)=\max(T) - \min(T) +1$ and prove the theorem by showing that $\range(T') \leq \eta$.
Since $T'$ can be written as a sequence of L-consecutive segments interleaved by gaps: $l_1,g_1,\ldots,l_{n-1}$, $g_{n-1},l_n$ ($n \geq 1$),
where $l_i$ is a segment and $g_i$ is a gap. Then, $\range(T')$
is calculated as $\Sigma_{i=1}^{i=n}|l_i| + \Sigma_{i=1}^{i=n-1} |g_i|$. Since $T'$
is valid, then $\Sigma_{i=1}^{i=n}|l_i| \geq K$. As $T'$ is minimum, if we remove the 
last $l_n$, the resulting sequence should not be valid. Let $K' = \Sigma_{i=1}^{i=n-1}|l_i|$, which
is the size of the first $(n-1)$ segments of $T'$. Then, $K' \leq K-1$.
Note that every $|l_i| \geq L$, thus $n \leq \lceil \frac{K'}{L} \rceil \leq \lceil \frac{K}{L} \rceil $. By
using the fact that every $|g_i| \leq G-1$, we achieve $\Sigma_{i=1}^{i=n-1} |g_i| \leq (n-1)(G-1)
\leq (\lceil \frac{K}{L} \rceil -1)(G-1)$. Next, we consider the difference between $K$ and $K'$, denoted by
$\Delta = K- K'$. To ensure $T'$'s validity, $l_n$ must equal to $\min(L, \Delta)$.
Then, $\Sigma_{i=1}^{i=n}|l_i| = K' + l_n = K - \Delta + \min(L, \Delta) \leq K - 1 + L$. We finish showing $\range(T') \leq \eta$.  Therefore, for any valid sequence $T$, it exists at least one valid subsequence with range no greater than $\eta$ and hence this pattern can be detected in a partition with $\eta$ snapshots.
\end{proof}

\vspace{-5mm}
\begin{algorithm}[h]
\small
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\ForAll{clusters $s$ in snapshot $S_t$} 
\label{code:ls-init-start}
\If{$|s| \geq M$}
\State $C\leftarrow C\cup \{\langle s, t \rangle \}$
\EndIf
\EndFor
\label{code:ls-init-end}
\ForAll{$S_j \in \{S_{t+1},\ldots,S_{t+\eta-1}\}$} \label{code:ls-sweep-starts}
	\State $N \gets \{\}$
	\ForAll {$(c,s) \in C \times S_j$} \label{code:ls-join-start}
		\State {$c' \gets \langle c.O \cap s.O, c.T \cup \{j\} \rangle$} \label{code:ls-join}
		\If {$c'.T$ is valid} 
			\State output $c'$
		\ElsIf{$|c'.O| \geq M$}
			\State $N\leftarrow N\cup \{c'\}$ \label{code:ls-m-prun}	
		\EndIf
	\EndFor \label{code:ls-join-ends}
	\ForAll {$c \in C$}
		\If{$j-\max(c.T)\geq G$}\label{code:ls-g-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
			\State output $c$, if $c$ is a valid pattern
		\EndIf  \label{code:ls-g-prune-ends}
		\If{$c$'s first segment is less than $L$}\label{code:ls-l-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
		\EndIf\label{code:ls-l-prune-ends}
	\EndFor
	\State $C\leftarrow C\cup N$
\EndFor\label{code:ls-sweep-ends}
\State output valid patterns in  $C$  \label{code:ls-valid-check}
\end{algorithmic}
\end{algorithm}

@@

The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}. We illustrate the workflow of the TRPM method using Figure~\ref{fig:trm} (c) and (d) with pattern
parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+ K + L - 1 = 5$. Therefore, 
in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set when sweeping snapshot $S_i$.
Initially, $C_1$ contains patterns with object sets in snapshot $S_1$.
As we sweep the snapshots, the patterns in $C_i$ grow. At snapshot $S_4$, the candidate
$\langle o_5,o_6 \rangle$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
and the next sweeping timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
Next, at snapshot $S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed. This is
because its local consecutive segment $(4)$ has only $1$ element,
which violates the $L$-consecutive constraint.
Finally, $\langle o_3,o_4 \rangle$ is the valid pattern and is returned. Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness. If $\eta$ is set to $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.

\begin{algorithm}[h]
\small
\caption{Temporal Replication and Parallel Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+K+L-1$
\State {\textit{---Map Phase---}}
\label{code:trm-map-start}
\ForAll{snapshots $S_t$}
	\ForAll{$i \in 1...{\eta-1}$}
		\State emit key-value pair $\langle \max(t-i,0), S_t \rangle$ 
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {\textit{---Partition and Shuffle Phase---}}
\label{code:trm-par-start}
\ForAll{key-value pairs $\langle t, S \rangle$} 
\State group-by $t$ and emit a key-value pair $\langle t, \lambda_t\rangle$, where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
\EndFor
\label{code:trm-par-end}
\State {\textit{---Reduce Phase---}}
\label{code:trm-red-start}
\ForAll{key-value pairs $\langle t,\lambda_t \rangle$}
\State call line sweep mining for partition $\lambda_t$
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

>>>>

\begin{figure*} [t]
\center
\includegraphics[width=0.85\textwidth]{trm.eps}
    \vspace{-0.5em}
\caption{Workflow of Temporal Replication and Parallel Mining (TRPM). (a) and (b) correspond to the first map-reduce stage which clusters objects in each snapshot.  (c) and (d) correspond to the second map-reduce stage, which uses TRPM to detect GCMP in parallel.}
\label{fig:trm}
\end{figure*}

\vspace{-3mm}
\section{Baseline: Temporal Replication and Parallel Mining}
\label{sec:trm}
In this section, we propose a baseline solution that resorts to Map-Reduce as a general, parallel and scalable paradigm for GCMP mining. The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}. There are two stages of map-reduce jobs connected in a pipeline manner. The first stage deals with spatial clustering of objects in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining phase. In particular, for the first stage, the timestamp is treated as the key in the map phase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phase. Finally, the reducers output clusters of objects in each snapshot, represented by a list of key-value pairs $\langle t, S_t  \rangle$, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.

@@

\begin{theorem}
\label{THM:RP_ETA}
$\eta = (\lceil \frac{K}{L} \rceil - 1)*(G-1)+K+L-1$ guarantees that no valid pattern is missing.
\end{theorem}
\vspace{-2em}
\begin{proof}
Given a valid pattern $P$, we can always find at least one valid subsequence of $P.T$ that is also valid. Let $T'$ denote the valid subsequence of $P.T$ with the minimum length. In the worst case, $T'=P.T$. We define $\range(T)=\max(T) - \min(T) +1$ and prove the theorem by showing that $\range(T') \leq \eta$.
Since $T'$ can be written as a sequence of L-consecutive segments interleaved by gaps: $l_1,g_1,\ldots,l_{n-1}$, $g_{n-1},l_n$ ($n \geq 1$),
where $l_i$ is a segment and $g_i$ is a gap. Then, $\range(T')$
is calculated as $\Sigma_{i=1}^{i=n}|l_i| + \Sigma_{i=1}^{i=n-1} |g_i|$. Since $T'$
is valid, then $\Sigma_{i=1}^{i=n}|l_i| \geq K$. As $T'$ is minimum, if we remove the 
last $l_n$, the resulting sequence should not be valid. Let $K' = \Sigma_{i=1}^{i=n-1}|l_i|$, which
is the size of the first $(n-1)$ segments of $T'$. Then, $K' \leq K-1$.
Note that every $|l_i| \geq L$, thus $n \leq \lceil \frac{K'}{L} \rceil \leq \lceil \frac{K}{L} \rceil $. By
using the fact that every $|g_i| \leq G-1$, we achieve $\Sigma_{i=1}^{i=n-1} |g_i| \leq (n-1)(G-1)
\leq (\lceil \frac{K}{L} \rceil -1)(G-1)$. Next, we consider the difference between $K$ and $K'$, denoted by
$\Delta = K- K'$. To ensure $T'$'s validity, $l_n$ must equal to $\min(L, \Delta)$.
Then, $\Sigma_{i=1}^{i=n}|l_i| = K' + l_n = K - \Delta + \min(L, \Delta) \leq K - 1 + L$. We finish showing $\range(T') \leq \eta$.  Therefore, for any valid sequence $T$, it exists at least one valid subsequence with range no greater than $\eta$ and hence this pattern can be detected in a partition with $\eta$ snapshots.
\end{proof}

\begin{algorithm}[h]
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\ForAll{clusters $s$ in snapshot $S_t$} 
\label{code:ls-init-start}
\If{$|s| \geq M$}
\State $C\leftarrow C\cup \{\langle s, t \rangle \}$
\EndIf
\EndFor
\label{code:ls-init-end}
\ForAll{$S_j \in \{S_{t+1},\ldots,S_{t+\eta-1}\}$} \label{code:ls-sweep-starts}
	\State $N \gets \{\}$
	\ForAll {$(c,s) \in C \times S_j$} \label{code:ls-join-start}
		\State {$c' \gets \langle c.O \cap s.O, c.T \cup \{j\} \rangle$} \label{code:ls-join}
		\If {$c'.T$ is valid} 
			\State output $c'$
		\ElsIf{$|c'.O| \geq M$}
			\State $N\leftarrow N\cup \{c'\}$ \label{code:ls-m-prun}	
		\EndIf
	\EndFor \label{code:ls-join-ends}
	\ForAll {$c \in C$}
		\If{$j-\max(c.T)\geq G$}\label{code:ls-g-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
			\State output $c$, if $c$ is a valid pattern
		\EndIf  \label{code:ls-g-prune-ends}
		\If{$c$'s first segment is less than $L$}\label{code:ls-l-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
		\EndIf\label{code:ls-l-prune-ends}
	\EndFor
	\State $C\leftarrow C\cup N$
\EndFor\label{code:ls-sweep-ends}
\State output valid patterns in  $C$  \label{code:ls-valid-check}
\end{algorithmic}
\end{algorithm}

@@

The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}. We illustrate the workflow of TRPM using Figure~\ref{fig:trm} (c) and (d) with pattern
parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+ K + L - 1 = 5$. Therefore, 
in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set when sweeping snapshot $S_i$.
Initially, $C_1$ contains patterns with object sets in snapshot $S_1$.
As we sweep the snapshots, the patterns in $C_i$ grow. At snapshot $S_4$, the candidate
$\langle o_5,o_6 \rangle$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
and the next sweeping timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
Next, at snapshot $S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed. This is
because its local consecutive segment $(4)$ has only $1$ element,
which violates the $L$-consecutive constraint.
Finally, $\langle o_3,o_4 \rangle$ is the valid pattern and is returned. Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness. If $\eta$ is set to $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.

\begin{algorithm}[h]
\caption{Temporal Replication and Parallel Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+K+L-1$
\State {\textit{---Map Phase---}}
\label{code:trm-map-start}
\ForAll{snapshots $S_t$}
	\ForAll{$i \in 1...{\eta-1}$}
		\State emit key-value pair $\langle \max(t-i,0), S_t \rangle$ 
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {\textit{---Partition and Shuffle Phase---}}
\label{code:trm-par-start}
\ForAll{key-value pairs $\langle t, S \rangle$} 
\State group-by $t$ and emit a key-value pair $\langle t, \lambda_t\rangle$, where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
\EndFor
\label{code:trm-par-end}
\State {\textit{---Reduce Phase---}}
\label{code:trm-red-start}
\ForAll{key-value pairs $\langle t,\lambda_t \rangle$}
\State call line sweep mining for partition $\lambda_t$
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

### 2016-09-10 sec5_spm.tex
Current Version

\begin{figure*}[t]
\centering
\includegraphics[width=0.85\textwidth]{spm.eps}
\caption{Star Partitioning and ApRiori Enumerator (SPARE). (a) Aggregated graph $G_A$ generated from Figure 1. (b) Five star partitions are generated from $G_A$. Star IDs are circled, vertexes and inverted lists are in the connected tables.
(c) Apriori Enumerator with various pruning techniques.}
\label{fig:star_partition}
\end{figure*}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{star-alt.eps}
\caption{Star partitioning with different vertex orderings.}
\label{fig:star-alt}
\end{figure}

@@

\begin{theorem}
\label{THM:SPM_LB}
Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be the value derived from a random vertex ordering. With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}
\begin{proof}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
If $G_A$ is dense, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
\begin{theorem}
\label{THM:SPM_LB_INC}
Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
\end{theorem}
\begin{proof}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
Hence, we can simply use object ID to determine the vertex ordering in our implementation.

@@

The maximal $G$-connected subsequence has the following two properties:
\begin{lemma}\label{lemma:union-property}
Suppose $\{T_1,T_2,\ldots,T_m\}$ is the set of all maximal $G$-connected subsequences of $T$, we have (1) $T_i\cap T_j=\emptyset$ for $i\neq j$ and (2) $T_1\cup T_2\cup\ldots\cup T_m=T$.
\end{lemma}
\begin{proof}
We assume $T_i\cap T_j\neq \emptyset$. Let $T_i=(T_i[1], T_i[2],\ldots,T_i[p])$ and $T_j= (T_j[1], T_j[2],\ldots,T_j[n])$. Suppose $T[x]$ is a timestamp occurring in both $T_i$ and $T_j$. Let $T[y]=\min\{T_i[1],T_j[1]\}$, i.e., the minimum timestamp of $T_i[1]$ and $T_j[1]$ occurs at the $y$-th position of sequence $T$. Similarly, we assume $T[z]=\max\{T_i[p], T_j[n]\}$. Apparently, the two subsequences $T[y:x]$ and $T[x:z]$ are $G$-connected because $T_i$ and $T_j$ are both $G$-connected. Then, sequence $(T_y,\ldots,T_x,\ldots,T_z)$, the superset of $T_i$ and $T_j$, is also $G$-connected. This contradicts with the assumptions that $T_i$ and $T_j$ are maximal $G$-connected subsequences.

@@

\begin{lemma}\label{lemma:subset-property}
%If $T_1$ is a subset of $T_2$, 
If $T_1 \subseteq T_2$, then for any maximal $G$-connected subsequence $T_1'$ of $T_1$, we can find a maximal $G$-connected subsequence $T_2'$ of $T_2$ such that %$T_1'$ is a subset of $T_2'$.
$T_1' \subseteq T_2'$.
\end{lemma}
\begin{proof}
Since $T_1' \subseteq T_1 \subseteq T_2 $, we know $T_1'$ is a $G$-connected subsequence of $T_2$. Based on Lemma~\ref{lemma:union-property}, we can find a maximal $G$-connected subsequence of $T_2$, denoted by $T_2'$, such that $T_1'\cap T_2'\neq \emptyset$. If there exists a timestamp $T_1'[x]$ such that $T_1'[x]\notin T_2'$, similar to the proof of case (1) in Lemma~\ref{lemma:union-property}, we can obtain a contradiction. Thus, all the timestamps in $T_1'$ must occur in $T_2'$.
\end{proof}

@@

\begin{definition}[Sequence Simplification]
Given a sequence $T$, the simplification procedure $\mathtt{sim}(T) =  g_{G,K} \cdot f_L(T) $ can be seen as a composite function with two steps: 
\begin{enumerate}
\item $f$-step: remove segments of $T$ that are not $L$-consecutive;
\item $g$-step: among the maximal $G$-connected subsequences of $f_L(T)$, remove those with size smaller than $K$.
\end{enumerate}
\end{definition}

@@

\begin{proof}
It is obvious that $\mathtt{sim}(T)$ is a one-to-one function. Given an input sequence T, there is a unique  $\mathtt{sim}(T)$. Let $T_p$ be a decomposable subset of $T$ and we prove the lemma by showing that $\mathtt{sim}(T)$ is a superset of $T_p$.

@@

\begin{proof}
We prove by contradiction. Suppose there exists a valid pattern $P_2$ such that $P_2.O \supseteq P.O$. It is obvious that $P_2.T \subseteq P.T$. Based on Definition 2, the following conditions hold: (1) $P_2.T$ is $G$-connected. (2) $|P_2.T| \geq K$ and (3) $P_2.T$ is $L$-consecutive. Note that the entire $P_2.T$ is $G$-connected. Thus, $P_2.T$ itself is the only maximal $G$-connected subsequence. Based on conditions (1),(2),(3) and Definition 6, $P_2.T$ is decomposable. Then, based on Lemma~\ref{lemma:decom-sim}, we know $\mathtt{sim}(T)\neq \emptyset$ because $P_2.T \subseteq P.T$ and $P_2.T$ is decomposable. This leads to a contradiction with $\mathtt{sim}(P.T)=\emptyset$.
\end{proof}

@@

Compared with TRPM, the SPARE framework does not rely on snapshot replication to guarantee correctness. In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
\begin{theorem}[Pattern Uniqueness]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
\end{theorem}
\begin{proof}
We prove by contradiction. Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set. Note that the center vertex of the star is associated with the minimum id. Let $o_i$ and $o_j$ be the center vertexes of the two partitions and we have $o_i=o_j$. However, $P_i$ and $P_j$ are different stars, meaning their center vertexes are different (i.e., $o_i\neq o_j$), leading to a contradiction. 
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\vspace{-5 mm}
\begin{proof}
See Appendix~\ref{apx:spm_correct}.
\end{proof}

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.85\textwidth]{spm.eps}
\vspace{-0.5em}
\caption{Star Partitioning and ApRiori Enumerator (SPARE). (a) Aggregated graph $G_A$ generated from Figure 1. (b) Five star partitions are generated from $G_A$. Star IDs are circled, vertexes and inverted lists are in the connected tables.
(c) Apriori Enumerator with various pruning techniques.}
\label{fig:star_partition}
\end{figure*}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.35\textwidth]{star-alt.eps}
\vspace{-0.5em}
\caption{Star partitioning with different vertex orderings.}
\label{fig:star-alt}
\end{figure}

@@

\begin{theorem}
\label{THM:SPM_LB}
Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be the value derived from a random vertex ordering. With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}
\begin{proof}
    \vspace{-0.5em}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
If $G_A$ is dense, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
\begin{theorem}
\label{THM:SPM_LB_INC}
Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
\end{theorem}
\begin{proof}
 \vspace{-0.5em}
See Appendix~\ref{apx:thm2proof}.
\end{proof}
Hence, we can simply use object ID to determine the vertex ordering in our implementation.

@@

The maximal $G$-connected subsequence has the following two properties:
\begin{lemma}\label{lemma:union-property}
Suppose $\{T_1,T_2,\ldots,T_m\}$ is the set of all maximal $G$-connected subsequences of $T$, we have (1) $T_i\cap T_j=\emptyset$ for $i\neq j$ and (2) $T_1\cup T_2\cup\ldots\cup T_m=T$.
\end{lemma}
\begin{proof}
 \vspace{-0.5em}
We assume $T_i\cap T_j\neq \emptyset$. Let $T_i=(T_i[1], T_i[2],\ldots,T_i[p])$ and $T_j= (T_j[1], T_j[2],\ldots,T_j[n])$. Suppose $T[x]$ is a timestamp occurring in both $T_i$ and $T_j$. Let $T[y]=\min\{T_i[1],T_j[1]\}$, i.e., the minimum timestamp of $T_i[1]$ and $T_j[1]$ occurs at the $y$-th position of sequence $T$. Similarly, we assume $T[z]=\max\{T_i[p], T_j[n]\}$. Apparently, the two subsequences $T[y:x]$ and $T[x:z]$ are $G$-connected because $T_i$ and $T_j$ are both $G$-connected. Then, sequence $(T_y,\ldots,T_x,\ldots,T_z)$, the superset of $T_i$ and $T_j$, is also $G$-connected. This contradicts with the assumptions that $T_i$ and $T_j$ are maximal $G$-connected subsequences.

@@

\begin{lemma}\label{lemma:subset-property}
%If $T_1$ is a subset of $T_2$, 
If $T_1 \subseteq T_2$, then for any maximal $G$-connected subsequence $T_1'$ of $T_1$, we can find a maximal $G$-connected subsequence $T_2'$ of $T_2$ such that %$T_1'$ is a subset of $T_2'$.
$T_1' \subseteq T_2'$.
\end{lemma}
\begin{proof}
 \vspace{-0.5em}
Since $T_1' \subseteq T_1 \subseteq T_2 $, we know $T_1'$ is a $G$-connected subsequence of $T_2$. Based on Lemma~\ref{lemma:union-property}, we can find a maximal $G$-connected subsequence of $T_2$, denoted by $T_2'$, such that $T_1'\cap T_2'\neq \emptyset$. If there exists a timestamp $T_1'[x]$ such that $T_1'[x]\notin T_2'$, similar to the proof of case (1) in Lemma~\ref{lemma:union-property}, we can obtain a contradiction. Thus, all the timestamps in $T_1'$ must occur in $T_2'$.
\end{proof}

@@

\begin{definition}[Sequence Simplification]
Given a sequence $T$, the simplification procedure $\mathtt{sim}(T) =  g_{G,K} \cdot f_L(T) $ can be seen as a composite function with two steps: 
\begin{enumerate}[nosep]
\item $f$-step: remove segments of $T$ that are not $L$-consecutive;
\item $g$-step: among the maximal $G$-connected subsequences of $f_L(T)$, remove those with size smaller than $K$.
\end{enumerate}
\end{definition}

@@

\begin{proof}
 \vspace{-0.5em}
It is obvious that $\mathtt{sim}(T)$ is a one-to-one function. Given an input sequence T, there is a unique  $\mathtt{sim}(T)$. Let $T_p$ be a decomposable subset of $T$ and we prove the lemma by showing that $\mathtt{sim}(T)$ is a superset of $T_p$.

@@

\begin{proof}
 \vspace{-0.5em}
We prove by contradiction. Suppose there exists a valid pattern $P_2$ such that $P_2.O \supseteq P.O$. It is obvious that $P_2.T \subseteq P.T$. Based on Definition 2, the following conditions hold: (1) $P_2.T$ is $G$-connected. (2) $|P_2.T| \geq K$ and (3) $P_2.T$ is $L$-consecutive. Note that the entire $P_2.T$ is $G$-connected. Thus, $P_2.T$ itself is the only maximal $G$-connected subsequence. Based on conditions (1),(2),(3) and Definition 6, $P_2.T$ is decomposable. Then, based on Lemma~\ref{lemma:decom-sim}, we know $\mathtt{sim}(T)\neq \emptyset$ because $P_2.T \subseteq P.T$ and $P_2.T$ is decomposable. This leads to a contradiction with $\mathtt{sim}(P.T)=\emptyset$.
\end{proof}

@@

Compared with TRPM, the SPARE framework does not rely on snapshot replication to guarantee correctness. In addition, we can show that the patterns derived from a star partition are unique and there would not be duplicate patterns mined from different star partitions.
\begin{theorem}[Pattern Uniqueness]
\label{LEM:SPM_CORRECT}
Let $Sr_i$ and $Sr_j$ ($i\neq j$) be two star partitions. Let $P_i$ (resp. $P_j$) be 
the patterns discovered from $Sr_i$ (resp. $Sr_j$). 
Then, $\forall p_i \in P_i, \forall p_j \in P_j$, we have $p_i.O \neq p_j.O$.
\end{theorem}
\begin{proof} \vspace{-0.5em}
We prove by contradiction. Suppose there exist $p_i \in P_i$ and $p_j \in P_j$ with the same object set. Note that the center vertex of the star is associated with the minimum id. Let $o_i$ and $o_j$ be the center vertexes of the two partitions and we have $o_i=o_j$. However, $P_i$ and $P_j$ are different stars, meaning their center vertexes are different (i.e., $o_i\neq o_j$), leading to a contradiction. 
\end{proof}

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}  \vspace{-0.5em}
See Appendix~\ref{apx:spm_correct}.
\end{proof}
